Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-18 surfaces-write-up/surface-write-up.tex
added dashes

Furthermore, similarly to the case of projective space, 
we will restrict to the case that $D$ is a divisor
for which both of its bi-degrees are positive. We now justify this
restriction. If either of the bidegrees of $D$ are negative,
then the canonical ring is concentrated in degree 0. If one of the
bidegrees is 0, say the first one is 0, then $R_D$ is isomorphic
to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
where $D'$ can be written as a sum of divisors whose degrees
are multiples of the second bidegree of $D$. Since the case of
$\bp^1$ has already been analyzed in \cite{canonical:dorney}, we
are justified in assuming that both bi-degrees of $D$ are positive.

>>>>

Furthermore, similarly to the case of projective space, 
we will restrict to the case that $D$ is a divisor
for which both of its bi-degrees are positive. We now justify this
restriction. If either of the bi-degrees of $D$ are negative,
then the canonical ring is concentrated in degree 0. If one of the
bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
where $D'$ can be written as a sum of divisors whose degrees
are multiples of the second bi-degree of $D$. Since the case of
$\bp^1$ has already been analyzed in \cite{canonical:dorney}, we
are justified in assuming that both bi-degrees of $D$ are positive.
